The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-10-12 paper.tex
minor cleanups and delete out-of-date outline
update authors and acknowledgements

% OUTLINE
% =======
%
% 1. Introduction
%
%   Here I will introduce the need for a new high-fidelity, low-frequency map of the sky. The
%   justifications are: 21 cm foreground mapping, galactic structure (?), others?
%
% 2. Observations
%
%   2.1 - Introduce the Owens Valley LWA
%   2.2 - Describe the 100 hour dataset
%   2.3 - Calibration strategy
%   2.4 - Source removal strategy
%   2.5 - Horizon RFI suppression strategy
%   2.6 - Beam fitting work
%   2.7 - Ionospheric conditions
%
% 3. Imaging
%
%   Give a brief overview of other widefield imaging algorithms. This should set the context for the
%   advantages of m-mode analysis.
%
%   3.1 - Introduce m-mode analysis imaging
%   3.2 - Describe my implementation of m-mode analysis on the ASTM
%   3.3 - L-curves (?)
%   3.4 - CLEAN
%
% 4. Results
%
%   Present sky maps with an estimate of the thermal noise in each pixel. Systematic errors will be
%   described in the following sub-sections.
%
%   4.1 - Horizon RFI
%   4.2 - Ionospheric effects
%   4.3 - Beam errors
%   4.4 - Peeling failures
%
% 5. Discussion
%
%   Compare with the Haslam map and Jayce's map.
%
% 6. Conclusion
%
% FIGURES
% =======
%
% * Antenna layout of the OVRO-LWA
% * Before/after snapshot image of the RFI removal
% * Image of the empirical beam (with source tracks)
% * Plot of ionospheric scintillation and refraction of an A-team source
% * Example L-curve
% * Zoom-in of the dirty PSF
% * Sky maps with their boot-strapped thermal noise estimates
% * (Model) image of the horizontal stripes that show up if the horizon RFI is not removed
% * (Model) image of the PSF distortion from ionospheric effects (scintillation, refraction)
% * (Model) image of the systematic errors in the map created from beam errors
% * (Model) image of the errors created from sporadic peeling failures

@@

@@

\author{Michael W. Eastwood}
\astrocaltech

\author{Marin M. Anderson}
\astrocaltech

\author{Ryan M. Monroe}
\astrocaltech

\author{Gregg Hallinan}
\astrocaltech

\author{Other People}
\affiliation{
    At some institution
}

%\author{Lincoln Greenhill}
%\affiliation{Harvard}
%
%\author{Hugh Garsden}
%\affiliation{Harvard}
%
%\author{Stephen Bourke}
%\affiliation{Chalmers}
%
%\author{Esayas B. Shume} % contributed ionosphere text
%\affiliation{Jet Propulsion Laboratory, 4800 Oak Grove Dr, Pasadena, CA 91109}

@@

%\subsection{The Global Sky Model}?
%\subsection{LWA1 Sky Survey}?

@@

\begin{figure*}[t]
    \centering
    \begin{tabular}{cc}
        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-4} &
        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-18} \\
        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-4} &
        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-18} \\
    \end{tabular}
    %\includegraphics[width=\textwidth]{figures/ionospheric-simulations/ionospheric-simulations}
    \caption{
        This figure illustrates the corrupting influence of the ionosphere at 36.528~MHz (left
        column) compared with 73.152~MHz (right column). Each panel shows the \textit{simulated} PSF
        for a source at the location of Cas~A.  Each panel illustrates the percent difference
        (relative to the peak flux of the uncorrupted PSF) due to including an ionospheric effect.
        In the top row, the simulated source scintillates using the measured light-curve for Cas~A
        in Figure~\ref{fig:scintillation}. In the bottom row, the simulated source is refracted from
        its true position using the measured refractive offsets for Cas~A in
        Figure~\ref{fig:scintillation}.
    }
    \label{fig:ionospheric-simulations}
\end{figure*}

@@

>>>>

@@

\newcommand{\eecaltech}{
    \affiliation{
        Department of Electrical Engineering,
        California Institute of Technology,
        1200 E California Blvd,
        Pasadena, CA 91125
    }
}

\newcommand{\ovro}{
    \affiliation{
        Owens Valley Radio Observatory,
        California Institute of Technology,
        Big Pine, CA 93513
    }
}

\newcommand{\jpl}{
    \affiliation{
        Jet Propulsion Laboratory,
        California Institute of Technology,
        4800 Oak Grove Dr,
        Pasadena, CA 91109
    }
}

\newcommand{\harvard}{
    \affiliation{
        Harvard-Smithsonian Center for Astrophysics,
        60 Garden Street,
        Cambridge, MA 02138
    }
}

@@

\author{Michael~W.~Eastwood} \astrocaltech
\author{Marin~M.~Anderson}   \astrocaltech
\author{Ryan~M.~Monroe}      \eecaltech
\author{Gregg~Hallinan}      \astrocaltech

% alphabetical by last name
\author{Lincoln~J.~Greenhill} \harvard
\author{T.~Joseph~W.~Lazio}   \jpl
\author{David~P.~Woody}       \ovro

%\author{Hugh Garsden}
%\affiliation{Harvard}
%
%\author{Stephen Bourke}
%\affiliation{Chalmers}
%
%\author{Esayas B. Shume} % contributed ionosphere text
%\affiliation{Jet Propulsion Laboratory, 4800 Oak Grove Dr, Pasadena, CA 91109}

@@

@@

\begin{figure*}[t]
    \centering
    \begin{tabular}{cc}
        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-4} &
        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/scintillation-18} \\
        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-4} &
        \includegraphics[width=\columnwidth]{figures/ionospheric-simulations/refraction-18} \\
    \end{tabular}
    \caption{
        This figure illustrates the corrupting influence of the ionosphere at 36.528~MHz (left
        column) compared with 73.152~MHz (right column). Each panel shows the \textit{simulated} PSF
        for a source at the location of Cas~A.  Each panel illustrates the percent difference
        (relative to the peak flux of the uncorrupted PSF) due to including an ionospheric effect.
        In the top row, the simulated source scintillates using the measured light-curve for Cas~A
        in Figure~\ref{fig:scintillation}. In the bottom row, the simulated source is refracted from
        its true position using the measured refractive offsets for Cas~A in
        Figure~\ref{fig:scintillation}.
    }
    \label{fig:ionospheric-simulations}
\end{figure*}

@@

Part of this research was carried out at the Jet Propulsion Laboratory, California Institute of
Technology, under a contract with the National Aeronautics and Space Administration, including
partial funding through the President's and Director's Fund Program.

This work has benefited from open-source technology shared by the Collaboration for Astronomy Signal
Processing and Electronics Research (CASPER).  We thank the Xilinx University Program for donations;
NVIDIA for proprietary tools, discounts, and donations; Digicom for collaboration on manufacture and
testing of DSP processors.

We thank the Smithsonian Astrophysical Observatory Submillimeter Receiver Lab for the collaboration
of its members.

Development, adaptation, and operation of the LEDA real-time digital signal processing systems at
OVRO-LWA has been supported in part by NSF grants AST/1106059, PHY/0835713, and OIA/1125087.
